Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Add images and enhance presentation formatting
- Introduces new images to improve the visual engagement of slides.
- Updates image references and HTML structure for better clarity.
- Adds comments for planned styling updates

:::: {.columns}
::: {.column width="50%"}
### Before BID:
<!-- Dashboard with overwhelming filters and complex tables -->
![](img/before_bid_dashboard.png){width="95%"}

@@

::: {.column width="50%"}
### After BID:
<!-- Streamlined dashboard with clear information hierarchy -->
![](img/after_bid_dashboard.png){width="95%"}

@@

:::: {.columns}
::: {.column width="60%"}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
:::

::: {.column width="40%"}
![The BID Framework](img/The_BID_framework.png)
::: 
::::

@@

::: {.r-stack}
![](img/reactable_example_1.png){width="75%"}
![](img/reactable_example_2.png){.fragment width="75%"}
![](img/reactable_example_3.png){.fragment width="75%"}
![](img/reactable_example_4.png){.fragment width="75%"}
:::

@@

::: {.r-stack}
![](img/echarts_example_1.png){width="75%"}
![](img/echarts_example_2.png){.fragment width="75%"}
![](img/echarts_example_3.png){.fragment width="75%"}
:::

@@

:::: {.columns .nonincremental}
::: {.column width="50%"}
#### Progress Framing:
![](img/progress_framing.png){width="90%"}
:::

::: {.column width="50%"}
#### Gap Framing:
![](img/gap_framing.png){width="90%"}
:::
::::

::: {.fragment}
**SoundPulse Results:** Marketing team preferred progress framing for stakeholder presentations, while product teams found gap framing more actionable for development priorities.
:::

@@

- "This slide demonstrates the power of framing in action - same exact data, completely different psychological impact"
- "Progress framing creates motivation and highlights achievement - 'We're 65% there!'"
- "Gap framing creates urgency and focuses on what remains to be done - '35% still to go!'"
- "This psychological principle has been demonstrated in countless studies"
- "Present a 90% survival rate vs. a 10% mortality rate - people react completely differently"
- When the results fragment appears: "At SoundPulse, this had real organizational impact"
- "Marketing needed to show progress to build confidence with stakeholders"
- "Product teams needed to focus on gaps to prioritize development resources"
- "The toggle feature meant both teams could use the same dashboard for different purposes"
- "This is why understanding psychological principles is so powerful for dashboard design"
- Interactive moment: "Think about your own dashboards - are you framing data in a way that drives the right decisions?"
- Transition: "Now let's talk about how we're making these principles accessible to every developer..."
:::

@@

- **Coming Soon (Phase 2-4):**
  - 🛠️ UI Component Library
  - 🤖 LLM Integration 
  - 📊 Testing and Validation Tools
:::

::: {.column width="40%"}
<!-- Console screenshot showing bid_concept output -->
![](img/bidux_console.png){width="95%"}
:::
::::

@@

- "We're not just sharing a framework - we're building tools to make it easy to adopt"
- "Our goal is to make these psychological principles accessible to every R developer"
- Emphasize this is open source - "We want this to become a community resource"
- Current features focus on documentation and knowledge
- Future features will include ready-to-use UI components with BID principles built in
- "The LLM integration will let you describe what you want in plain language"
- "Think of {bidux} as your behavioral science co-pilot for dashboard development"
- "This is in active development - we welcome contributors and collaborators"
:::

@@

# Currently available:
# 1. Concept dictionary functionality
concepts <- bid_concepts()
print(concepts)

processing_fluency <- bid_concept("Processing Fluency")
print(processing_fluency)

# 2. Stage documentation (piped workflow)
project_docs <- bid_notice(
  problem = "Dashboard overload", 
  theory = "Cognitive Load Theory",
  evidence = "User testing results"
) |>
  bid_interpret(
    central_question = "How to simplify?",
    data_story = list(hook = "Too complex", context = "Many tabs")
  )

# Coming in Phase 2: UI component library with templates
# ui <- bid_structure(
#   layout = "dual_process",
#   concepts = c("default_effect", "principle_of_proximity")
# )
```

>>>>

:::: {.columns .nonincremental .fragment}
::: {.column width="50%"}
### Before BID:
<!-- Dashboard with overwhelming filters and complex tables -->
![](img/before-bid.png){width="95%"}

@@

::: {.column width="50%" .fragment}
### After BID:
<!-- Streamlined dashboard with clear information hierarchy -->
![](img/after-bid.png){width="95%"}

@@

:::: {.columns}
::: {.column width="60%"}
![](img/bid-framework.png)
:::

::: {.column width="40%"}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
::: 
::::

@@

::: {.r-stack}
![](img/reactable_example_1.png){width="75%"}
![](img/reactable_example_2.png){.fragment width="75%"}
![](img/reactable_example_3.png){.fragment width="75%"}
![](img/reactable_example_4.png){.fragment width="75%"}

<!-- Commenting to show suggestion placeholders -->
<!-- ![](img/Screenshot_examples_main_1.png){width="75%"}
![](img/Screenshot_examples_main_2.png){.fragment width="75%"}
![](img/Screenshot_examples_main_3.png){.fragment width="75%"}
![](img/Screenshot_examples_main_4.png){.fragment width="75%"} -->
:::

@@

::: {.r-stack}
![](img/echarts_example_1.png){width="75%"}
![](img/echarts_example_2.png){.fragment width="75%"}
![](img/echarts_example_3.png){.fragment width="75%"}

<!-- Commenting to show suggestion placeholders -->
<!-- ![](img/Screenshot_examples_Deep_Dives_1.png){width="75%"}
![](img/Screenshot_examples_Deep_Dives_2.png){.fragment width="75%"}
![](img/Screenshot_examples_Deep_Dives_3.png){.fragment width="75%"} -->
:::

@@

:::: {.columns .nonincremental}
::: {.column width="50%" .fragment}
#### Progress Framing:
<!-- going to change these screenshots to be more focused on a single bar -->
![](img/progress-frame.png){width="90%"}

- Motivates by highlighting achievement
- Creates positive momentum
- Supports incremental improvement
:::

::: {.column width="50%" .fragment}
#### Gap Framing:
<!-- going to change these screenshots to be more focused on a single bar -->
![](img/gap-frame.png){width="90%"}

- Creates urgency to address shortfall
- Highlights areas needing improvement
- May trigger risk-avoidance behaviors
:::
::::

@@

- "This slide demonstrates the power of framing in action - same exact data, completely different psychological impact"
- "Progress framing creates motivation and highlights achievement - 'We're 65% there!'"
- "Gap framing creates urgency and focuses on what remains to be done - '35% still to go!'"
- "This psychological principle has been demonstrated in countless studies"
- "Present a 90% survival rate vs. a 10% mortality rate - people react completely differently"
- "At SoundPulse, this had real organizational impact"
    - Marketing team preferred progress framing for stakeholder presentations, while product teams found gap framing more actionable for development priorities.
- "Marketing needed to show progress to build confidence with stakeholders"
- "Product teams needed to focus on gaps to prioritize development resources"
- "The toggle feature meant both teams could use the same dashboard for different purposes"
- "This is why understanding psychological principles is so powerful for dashboard design"
- Interactive moment: "Think about your own dashboards - are you framing data in a way that drives the right decisions?"
- Transition: "Now let's talk about how we're making these principles accessible to every developer..."
:::

@@

- **Coming Soon (Phases 2-4):**
  - 🛠️ UI Component Library
  - 🤖 LLM Integration 
  - 📊 Testing and Validation Tools
:::

::: {.column width="40%"}
<!-- need to either update image or replace with something like the repo README -->
![](img/bid_concept-output.png){width="95%"}
:::
::::

@@

- "We're not just sharing a framework - we're building tools to make it easy to adopt"
- "Our goal is to make these psychological principles accessible to every R developer"
- Emphasize this is open source - "We want this to become a community resource"
- Current features focus on documentation and knowledge
- Future features will include ready-to-use UI components with BID principles built in
- "The LLM integration will let you describe what you want in plain language"
- "Think of {bidux} as your behavioral science assistant for dashboard development"
- "This is in active development - we welcome contributors and collaborators"
:::

@@

# 1. Concept dictionary functionality
processing_fluency <- bid_concept("Processing Fluency")
print(processing_fluency)

# 2. Stage documentation (piped workflow)
project_docs <- bid_notice(
  problem = "Dashboard overload", 
  theory = "Cognitive Load Theory",
  evidence = "User testing results"
) |>
  bid_interpret(
    central_question = "How to simplify?",
    data_story = list(hook = "Too complex", context = "Many tabs")
  )
print(processing_fluency)
```
